Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/presentasjon.Rmd
Changing slides

## <br> Workarounds... 
- Proff.no: It maaay be legal to manually download the websites as HTML instead of scraping 
- Brønnøysund: We attempted to request a temporary access to XML documents
<!--# We received some sample XML data from Statistics Norway -- we did not talk to Brønnøysund at all-->

@@

@@

----
```{r, out.height="500", out.width="500", fig.align='center'}
knitr::include_graphics("Images/tenke.png")

>>>>

## <br> Workarounds... 
- Proff.no: It maaay be legal to manually download the websites as HTML instead of scraping 
- Brønnøysund: We attempted to request a temporary access to XML documents

@@

# Findings

# Limitations and steps forward

@@

## {data-background="Images/tenke.png" data-background-size=cover}
